Coherent optical association of a single molecule

### 2020-09-20 paper.tex
Update on Overleaf.

While optical Raman transfer of atoms to molecules utilizing an electronic excited state has been shown previously\todo{cite}. Those demonstrations were  incoherent  where the signal comes from loss of population (and therefore more like spectroscopy and the transferred molecules cannot be further utilized). The challenge lies at  achieve high enough Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
 Previous experiments use weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency. However, this choice of state also increases the scattering during the transfer process for two reasons.
Firstly, since for a typical molecular potential the spacing between states
decreases with increasing vibrational levels,
a weakly bound excited molecular state limits maximum usable detuning and therefore the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
Secondly, due to size similarity, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
The rate of such scattering process is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
% This further increases the scattering rate for a weakly bond excited state.
Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states. As a result, we use a deeply bound molecular excited state to drive the Raman transition. (mention the trend, also v=12 will work as similarly as v=0)

>>>>

While optical Raman transfer of atoms to molecules utilizing an electronic excited state has been shown previously\cite{Wynar2000,Rom2004}. Those demonstrations were  incoherent  where the signal shows resonance loss of population and the transferred molecules cannot be further utilized(need to improve). The challenge lies at  achieve high enough Raman Rabi frequency to drive this transition due to the wavefunction size mismatch with the excited molecular state.
 Previous experiments use weakly bound molecular excited states in the Raman transition to increase the Raman Rabi frequency. However, this choice of state also increases the scattering during the transfer process for two reasons.
Firstly, since for a typical molecular potential the spacing between states
decreases with increasing vibrational levels,
a weakly bound excited molecular state limits maximum usable detuning and therefore the effectiveness of scattering reduction by increasing the detuning for the Raman transition.
Secondly, due to size similarity, the weakly bound molecular ground state has a strong coupling with the atomic excited state which contributes significantly to the total scattering rate.
The rate of such scattering process is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold. (Should we also mention scattering of the atomic initial state too? This should affect the Raman process as well)
% This further increases the scattering rate for a weakly bond excited state.
Based on these considerations, we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in figure (1....), despite a higher Raman Rabi frequency at the same detuning, using a weakly bound intermediate state results in a much higher scattering rate and ultimately a smaller Rabi frequency to scattering rate ratio as compared to deeply bound states. As a result, we use a deeply bound molecular excited state to drive the Raman transition. (mention the trend, also v=12 will work as similarly as v=0)
